Outbreak Threshold Detection

### 2023-08-16 notebooks/Julia/simulation-detection.qmd
Add basic gillespie and ODE SIR models for debugging purposes Translate Tiffany's code to calculate beta into Julia. Currently works, but it looks like it only works for a 1x1 contact matrix i.e. when there is only one group
Rename beta vars to use text rather than symbols
Want to be clearer about meaning and some editors etc don't render unicode characters

μ = 1
β = 1000
σ = 365/8
γ = 365/5
ε = 100
p = (β, σ, γ, μ, ε)
```

```{julia}
x = 0:0.1:10
fig = lines(x, 0.5 .* (sin.(2pi .* x) .+ 1))
vlines!(collect(0:1:10); color = (:red, 0.5), linestyle = :dash)
fig
```

```{julia}
# 0.5 .* (sin.(2π .* x) .+ 1)
expose_rate(u, p, t) = p[1] * 0.5 * (sin(2π * t) + 1) * u[1] * u[2]/ (u[1] + u[2] + u[3] + u[4])  # β * ϕ * S * I / N
function expose_affect!(integrator)
    integrator.u[1] -= 1         # S -> S - 1
    integrator.u[2] += 1         # E -> E + 1
    nothing
end

>>>>

μ = 1
beta = 1000
σ = 365/8
γ = 365/5
ε = 100
p = (beta, σ, γ, μ, ε)
```

```{julia}
x = 0:0.01:2
fig = lines(x, 0.5 .* (sin.(2pi .* x) .+ 1))
vlines!(collect(0:1:2); color = (:red, 0.5), linestyle = :dash)
fig
```

```{julia}
# 0.5 .* (sin.(2π .* x) .+ 1)
expose_rate(u, p, t) = p[1] * 0.5 * (sin(2π * t) + 1) * u[1] * u[2]/ (u[1] + u[2] + u[3] + u[4])  # beta * ϕ * S * I / N
function expose_affect!(integrator)
    integrator.u[1] -= 1         # S -> S - 1
    integrator.u[2] += 1         # E -> E + 1
    nothing
end
